Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-22 paper/sections/proof-reconstruction.tex
[ paper ] buildOr added.

\begin{equation}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
  \RightLabel{∧-proj$_{i}$}
  \UnaryInfC{$Γ ⊢ φ_{i}$}
  \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
  \AxiomC{$conjunct(φ_{i}, ψ) ≡ ψ$}
  \RightLabel{subst}
  \BinaryInfC{$Γ ⊢ ψ$}
  \end{bprooftree}
\end{equation}

Finally, in the latter case, by using the hypothesis, $Γ ⊢ φ$,
we complete the proof.

Note that $conjunct$ function and also its theorem are well defined structural recursions, since φ₁ and φ₂ in the argument from the definition are structurally smaller than φ.
\end{proof}

\emph{Clausification.}

>>>>

\begin{equation}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
  \RightLabel{∧-proj$_{i}$}
  \UnaryInfC{$Γ ⊢ φ_{i}$}
  \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
  \AxiomC{$conjunct(φ_{i}, ψ) ≡ ψ$}
  \RightLabel{subst}
  \BinaryInfC{$Γ ⊢ ψ$.}
  \end{bprooftree}
\end{equation}

The last statement follows by using the hypothesis and the proof is complete.
\end{proof}

% To deal with nested conjunctions and nested disjunctions, we follow a similar strategy mainly described in \citeauthor{bohme2010}~\cite{bohme2010}.

First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and in a similar way with disjunctions,
we define $rdisj$ function, to convert a general disjunction to a be right-associative disjunction.

\begin{equation}
\label{eq:rconj-def}
\begin{split}
&rconj(φ) =\begin{cases}
ψ₁ ∧ rconj(ψ₂ ∧ φ₂) &\text{if }φ = φ₁ ∧ φ₂\text{, } ψ≡rconj(φ₁),\\
&\text{and }ψ ≡ ψ₁ ∧ ψ₂,\\[3mm]
ψ ∧ rconj(φ₂)  &\text{if }φ = φ₁ ∧ φ₂\text{, } ψ≡rconj(φ₁),\\
φ &\text{otherwise.}
\end{cases}
\end{split}
\end{equation}

\begin{equation}
\begin{split}
\label{eq:buildOr}
buildOr(φ, ψ) =
\begin{cases}
ψ &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } buildOr(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2,\\
ψ &\text{if } φ ≡ ψ,\\
φ &\text{otherwise.}
\end{cases}
\end{split}
\end{equation}
